Analysis of the included studies

### 2023-05-15 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Remove word_output
Styled the script

---
title: "Analysis of the included studies"
output:
  # word_document:
  #   toc: yes
  pdf_document:
    toc: yes
    keep_tex: yes
    fig_crop: no
---

@@

knitr::kable(studies_per_collab_type, 
             caption = 'Number of studies per collaboration type (Human VPDs)',
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

>>>>

---
title: "Analysis of the included studies"
output:
  pdf_document:
    toc: yes
    keep_tex: yes
    fig_crop: no
---

@@

knitr::kable(studies_per_collab_type, 
             caption = 'Number of studies per collaboration type (Human VPDs)',
             format = "latex", 
             booktabs = TRUE
             ) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```
